RADseq Works in Primates, Dammit.

### 2012-12-10 paper/paper.tex
Changed pipeline to incorporate SE data.

\title{RADseq Works in Primates, Dammit.}
\author{
        Christina M. Bergey
			\and
			Andrew S. Burrell
			\and
			Luca S.J. Pozzi
			\and
			Todd R. Disotell
	}
\date{\today}

@@

\begin{abstract}
\ldots Blah, blah, blah, RADseq, blah, blah, Cercopithecoidea. \ldots
\end{abstract}

@@

%\paragraph{Analysis Pipeline - Inferring Phylogeny}
%\begin{itemize}
%	\item Using Stacks? 
%	\item Using method like cichlid people?
%	\item Using method like Rubin et al %http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0033394
%\end{itemize}

@@

\begin{table}[h]
\caption{Individual Sample Information}
\begin{center}
	\small
	\begin{tabular}{ p{3cm} || l || p{1.75cm} | p{1.75cm} || p{1.75cm} | p{1.75cm} | l }
		\hline
		Taxon & Source & \# Reads & \# Filtered Reads & \# Loci $\ge 1$ Read & \# Loci $\ge 3$ Reads & \# SNPs \\ \hline\hline
		\textcolor{red}{Langur?} & \textcolor{red}{Unknown} & 1,367,050 & 306,248 & 47,516 & 24,052 & 363,501 \\ \hline
		\emph{Allenopithecus nigroviridis} & \textcolor{red}{Unknown} & 1,325,558 & 447,279 & 62,824 & 40,244 & 356,750 \\ \hline
		\emph{Macaca mulatta} & \textcolor{red}{Unknown} & 481,376 & 234,659 & 77,798 & 32,302 & 279,350 \\ \hline
		\emph{Cercocebus torquatus atys} & \textcolor{red}{Unknown} & 297,290 & 124,700 & 48,440 & 13,104 & 319,766 \\ \hline
		\emph{Papio anubis\textcolor{red}{?}} & \textcolor{red}{Unknown} & 743,556 & 313,676 & 74,582 & 39,062 & 316,118 \\ \hline
		\emph{Theropithecus gelada} & \textcolor{red}{Unknown} & 1,911,030 & 603,024 & 68,440 & 50,656 & 366,097 \\
		\hline
	\end{tabular}
\end{center}
\end{table}

@@

@@

\begin{itemize}
	\item SNP info from merged analysis
	\item SNP Venn diagram?
	\item Count orthologous SNPs shared between individuals
	\item VCFtools vcf-compare for this job
\end{itemize}

\section{Discussion}
\begin{itemize}
	\item RADseq is viable tool for researcher interested in primate phylogenetics, pop. gen.
	\item Enzyme choice allows control over coverage, number of individuals, number of loci.
	\item Potential problems with RADseq method
	\item Promise for primatology
\end{itemize}

\section{Acknowledgements}
Acknowledgements

>>>>

\title{RADseq Works in Primates, Dammit.}
\author{
        Christina M. Bergey
			\and
			Luca Pozzi
			\and
			Todd R. Disotell
			\and
			Andrew S. Burrell
	}
\date{\today}

@@

\begin{abstract}
\ldots (This is the blurb from the email.) Our paper is an introduction to a 2nd generation sequencing technique for typing thousands of genome-wide markers from non-model organisms. Though it's been used in other taxa, this would be the first published application to primates. We demonstrate it with six Cercopithecoids and discuss its promise for doing mutli-locus population genetics in primates. \ldots
\end{abstract}

@@

\paragraph{Analysis Pipeline - Inferring Phylogeny}
\begin{itemize}
	\item Using method like cichlid people?
	\item Using method like Rubin et al? 
	\item Concatenated SNPs (not indels) into alignment. 
	\item Dimensions = 6 x ???
\end{itemize}

@@

\begin{table}[h]
\caption{Individual Sample Information}
\begin{center}
	\small
	\begin{tabular}{ p{3cm} || l || p{1.75cm} | p{1.75cm} || p{1.75cm} | p{1.75cm} | l }
		\hline
		Taxon & Source & \# Reads & \# Filtered Reads & \# Loci $\ge 1$ Read & \# Loci $\ge 3$ Reads & \# SNPs \\ \hline\hline
		\emph{Semnopithecus entellus} & \textcolor{red}{Unknown} & 1,367,050 & 306,248 & 47,516 & 24,052 & 363,501 \\ \hline
		\emph{Allenopithecus nigroviridis} & \textcolor{red}{Unknown} & 1,325,558 & 447,279 & 62,824 & 40,244 & 356,750 \\ \hline
		\emph{Macaca mulatta} & \textcolor{red}{Unknown} & 481,376 & 234,659 & 77,798 & 32,302 & 279,350 \\ \hline
		\emph{Cercocebus torquatus atys} & \textcolor{red}{Unknown} & 297,290 & 124,700 & 48,440 & 13,104 & 319,766 \\ \hline
		\emph{Papio anubis\textcolor{red}{?}} & \textcolor{red}{Unknown} & 743,556 & 313,676 & 74,582 & 39,062 & 316,118 \\ \hline
		\emph{Theropithecus gelada} & \textcolor{red}{Unknown} & 1,911,030 & 603,024 & 68,440 & 50,656 & 366,097 \\
		\hline
	\end{tabular}
\end{center}
\end{table}

@@

\begin{itemize}
	\item Pairwise comparisons between individuals? Like X orthologous regions shared between Papio and Thero?
\end{itemize}

@@

\begin{itemize}
	\item SNP info from merged analysis
	\item SNP Venn diagram?
	\item Count orthologous SNPs shared between individuals. Pairwise?
\end{itemize}

\section{Discussion}
\begin{itemize}
	\item RADseq is viable tool for researcher interested in primate phylogenetics, pop. gen.
	\begin{itemize}
		\item Cheap and easy to create libraries. Competent lab can do it in two days. (Ha!)
		\item Multiplexing is great for pop gen studies.
		\item Enzyme choice allows control over coverage, number of individuals, number of loci.
	\end{itemize}
	\item Potential problems with RADseq method
	\item Promise for primatology
\end{itemize}

\section{Acknowledgements}
\begin{itemize}
	\item NYU Med School folk
	\item \textcolor{red}{Grants?}
\end{itemize}
